---
title: "Lab2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
boxplot(choco$Rating)
plot(choco$Rating,choco$Cocoa.Pct, xlab = "Ratings", ylab = "Cocoa Percentage", pch = 2, cex=2)
```
Indiviual
1. How are ratings distributed? Don't forget to mention outliers, if there are any.

Ratings are centered around 3.5, and the 50% of the data is between about 3 - 3.75. There are 4 outliers, one above the mean and three below.

2. Do ratings depend on the cacao percentage of a chocolate bar? 
No, the ratings do not depend on the cacao percentage.

3. What class is the variable representing company locations? How is this different from a 'character' variable? (You do not need to produce a graphic for this question.)
String, it can contain multiple letters instead of just one.

Team
```{r, eval=TRUE}
recent_rating = choco[choco$Review.Date>2011,]
#Gets ratings of only reviews after 2011

unique(recent_rating$Company.Location) # NOTICE: how many countries are listed but how many levels are there? 
#Gets only the unique locations from the reviews

recent_rating$Company.Location = droplevels(recent_rating$Company.Location)
#Deletes all repeated locations

head(recent_rating)
#Displays first couple values of recent rating

cross_table = table(recent_rating$Review.Date,recent_rating$Company.Location)
#Adds the recent rating and location tables together
cross_table
#Displays table

which(cross_table[1,]!=0 & cross_table[2,]!=0 & cross_table[3,]!=0 & cross_table[4,]!=0 & cross_table[5,]!=0)
#Shows all non zero entries

france_recent = subset(recent_rating,Company.Location =='France')
#Creates a subset of only French entries
uk_recent = subset(recent_rating,Company.Location =='U.K.')
#Creaes a subset of only U.K. entries
germany_recent = subset(recent_rating,Company.Location=='Germany')
#Creates a subset of only Germany

par(mfrow=c(2,2))
#Sets parameters for graphs
color1 = ifelse(france_recent$Rating >median(france_recent$Rating), 'blue', 'green')
#Sets colors for graph
plot(france_recent$Cocoa.Pct ~ france_recent$Review.Date,ylim=c(50,90),col=color1,pch=18,cex=1.5,xlab="Review Date", ylab= "Cocoa Percentage", main= "France") 
#Plots France's data in a scatter plot
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('blue','green'),pch=18)
#Adds legend


color2 = ifelse(uk_recent$Rating >median(uk_recent$Rating), 'purple', 'red')
#Sets colors for graph
plot(uk_recent$Cocoa.Pct ~ uk_recent$Review.Date,ylim=c(50,90),col=color2,pch=18,cex=1.5, xlab="Review Date", ylab= "Cocoa Percentage", main= "UK")
#Plots UK's data in a scatter plot
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('purple','red'),pch=18)
#Adds legend

color3 = ifelse(germany_recent$Rating > median(germany_recent$Rating), 'orange', 'yellow')
#Sets colors for graph
plot(germany_recent$Cocoa.Pct ~ germany_recent$Review.Date,ylim=c(50,90),col=color3,pch=18,cex=1.5,xlab="Review Date", ylab= "Cocoa Percentage", main= "Germany") 
#Plots Germany's data in a scatter plot
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('orange','yellow'),pch=18)
#Adds legend
```


2 \. Click Zoom on the Rstudio window (under Plots) to see the plot more clearly. How do you think the plot produced from the code above can be improved? Recommend at least one possible improvement. 
Making the graphs the width of the screen would help visibility.

3 \. How does the **number** of ratings (not the actual value of the rating) depend on the year? Use graphics to answer this question.
```{r}
plot(choco$Review.Date,choco$Rating, xlab = "Date", ylab = "Rating", pch = 2, cex=2)
```

The number of ratings decreases slightly through the years.

4 \. How do ratings compare across different company locations? Focus on the three locations with the most ratings. Hint: the function `sort()` might come in handy here.

```{r}
sort(choco$Company.Location)
plot(choco$Company.Location,choco$Rating, xlab = "Location", ylab = "Rating", pch = 2, cex=2)
```

The ratings are fairly similarly spread out among most companies, being around the 3-4 range, except for Russia which is very spread out through the 2-4 range. 

5 \. Brainstorm and write down an interesting question that can be answer from the dataset. The question should not duplicate the questions above.

Does the review date change the spread of ratings?

6.
```{r}
sort(choco$Review.Date)
plot(choco$Review.Date,choco$Rating, xlab = "Date", ylab = "Rating", pch = 2, cex=2)
```
More 5 star ratings were given in 2006 and 2007 than any other year. In recent years, the spread of ratings has decreased. 


